\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage[normalem]{ulem}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

%\pagenumbering{arabic}
\pagenumbering{gobble}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contact Info
\begin{center}
	{\Large \scshape Tyler Alamo Port}
\end{center}
\vspace*{-2pt}
\hspace{7.25mm} \faGithub \hspace{0.25mm} \textbf{\href{https://github.com/tyler274}{github.com/tyler274}} \hspace{7.25mm} \faLinkedinSquare \hspace{0.25mm} \textbf{\href{https://linkedin.com/in/tyler-port-9a795455/}{linkedin.com/in/tyler-port-9a795455}} \\
\vspace*{3pt}  \hspace{12.25mm} \faEnvelope \hspace{0.1mm} \textbf{\href{mailto:tyler274port@gmail.com}{tyler274port@gmail.com}} \hspace{8.25mm} \faMobile : \textbf{\href{tel:15167767470}{+1 (516) 776-7470}}\\
\vspace{1pt}
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Work and Experience}
%\smallskip
\begin{body}
	\vspace{14pt}
	% \textbf{Caltech.}, \emph{Teaching Assistant in Computer Science} \hfill
	% \emph{Jan 2022 - March 2022}\\
	% \vspace*{-3pt}
	% \begin{itemize} \itemsep -0pt %reduce space between items
	% 	\item Taught Rust programming for the CS11 Rust track.
	% 	\item Held office hours and graded assignments.
	% 	\item Translated and reimplemented assignments for CS24 (Operating
	% 	      Systems) from C to Rust.
	% \end{itemize}
	% \vspace*{-2pt}

	% \textbf{Caltech.}, \emph{Teaching Assistant in Computer Science} \hfill
	% \emph{Jan 2021 - March 2021}\\
	% \vspace*{-3pt}
	% \begin{itemize} \itemsep -0pt %reduce space between items
	% 	\item Taught relational database theory and use with Structured Query Language
	% 	      (SQL) in CS121.
	% 	\item Held office hours and graded assignments.
	% \end{itemize}
	% \vspace*{-2pt}

	\textbf{Caltech}, \emph{Lecturer and Teaching Assistant in Computer Science} \hfill \emph{April 2018 - June 2022}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -0pt %reduce space between items
		\item Lectured, held office hours, developed material, and graded Nvidia CUDA assignments for CS179 GPU Programming.
		\item Taught relational database theory and use with Structured Query Language
		      (SQL) in CS121.
		\item Taught Rust programming for the CS11 Rust language workshop.
		\item Translated and reimplemented assignments for CS24 (Operating
		Systems) from C to Rust.
	\end{itemize}
	\vspace*{-2pt}

	\textbf{North American Partners in Anesthesia.}, \emph{Operations Intern} \hfill
	\emph{Dec 2019 - August 2020}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -0pt %reduce space between items
		\item Automated inter-database information validation between Cactus and the
		      National Provider Database.
		\item Assisted with automation testing and development interfacing with GUI based terminal
		      systems for healthcare data processing.
	\end{itemize}
	\vspace*{-2pt}

	\textbf{Tinder Inc.}, \emph{Operations Intern} \hfill \emph{June 2018 - August 2018}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -0pt %reduce space between items
		\item Researched and implemented a configuration that walked the graph of
		microservice dependencies to determine what services were degraded based on a dependency.
		\item Used and extended Grafana and Prometheus to automate status page generation.
	\end{itemize}
	\vspace*{-2pt}


	\textbf{NASA Jet Propulsion Lab}, \emph{Year Round Intern} \hfill \emph{January 2018 - June 2018}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -0pt %reduce space between items
		\item Worked on trajectory finding and visualization for the Europa Lander mission.
	\end{itemize}
	\vspace*{-2pt}

	\textbf{DoubleVerify Inc.}, \emph{Bot Fraud Analyst Intern} \hfill \emph{June 2015 - September 2015}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -0pt %reduce space between items
		\item Infected machines with malware and analyzed the collected network traffic for evidence of botnet based ad fraud.
		\item Researched botnet forums for new developments in the field, especially the prevalence of voluntary botnets known as traffic exchanges, and YouTube based revenue generation.
	\end{itemize}
	\vspace*{-2pt}

	\textbf{KarmaFleet}, \emph{Software Developer and Systems Administrator} \hfill \emph{January 2015 - Febuary 2016}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -0pt %reduce space between items
		\item Wrote a web application in Flask (Python) for recruitment, customer relations management, human resources, and internal affairs. Included automated testing and continuous integration.
		\item Maintained multiple applications for VOIP, market management, expenses, and claims.
		\item Containerized application development and deployment.
		\item Linux server setup, administration, and maintenance.
	\end{itemize}
	\vspace*{-2pt}

	\textbf{GLO Gaming}, \emph{Office IT} \hfill \emph{September 2012 - September 2014}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -0pt %reduce space between items
		\item Built office storage server and network infrastructure including JUNOS configuration.
		\item Helped develop Salesforce integrations.
		\item Built and maintained OpenVPN and NAS instances.
	\end{itemize}
	\vspace*{-2pt}

	\smallskip
	\vspace*{-3pt}
	\vspace*{-5pt}
	\smallskip
\end{body}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Education
	\header{Education}
	%\smallskip
	\begin{body}
		\vspace{16pt}
		\textbf{California Inst. of Technology [Caltech]}{}, \emph{B.S. in CS} \hfill \emph{September 2015 - June 2022}{} \\
		\vspace{-3pt}
		\begin{itemize} \itemsep -0pt
			\item Studied Computer Science with a focus on low level GPU Programming for
			parallelizing and accelerating a variety of algorithms. Taught and composed material for
			several courses.
		\end{itemize}
	\end{body}

	\smallskip
	\vspace*{-3pt}



\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}
\smallskip
\begin{body}
	\vspace{14pt}
	\begin{itemize} \itemsep -0pt

		\item \uline{Lanugages:} \textbf{Rust}, Python, C/C++, CUDA/OpenCL/HIP, C\#, Haskell, VHDL, OCaml, Javascript, SQL, Java/Kotlin, Mathematica.

		\item \uline{Platforms/Technology:} Linux (Gentoo, Arch, RHEL/Fedora,
		Debian/Ubuntu), Windows, MacOS,
		      BSD, FPGA (Intel, AMD), Git.
		\item \uline{Specialties:} GPU programming, functional programming, computer graphics, relational database design and managagement, graph theory, systems administration, DevOps.
	\end{itemize}
\end{body}

\end{document}
